%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {C++ Develop Engineer} % Job title
    {Yeahsen(Guangzhou Yuechen Technology Co., Ltd.)} % Organization
    {GuangZhou, China} % Location
    {Mar. 2023 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Profoundly expand the game architecture, leading the development of new projects, infusing fresh vitality into the adventurous world of One Piece.} 
        \item {Build bridges across the seas, facilitating efficient communication for overseas business, ensuring seamless integration of the game’s globalization.} 
        \item {Accurately assess project performance, dedicated to optimization and enhancement, guaranteeing a smooth gaming experience.} 
        \item {Organize UI resources, optimize the process of path arrangement and replacement, enhancing visual presentation.} 
        \item {Develop and refine code specification standards, ensuring efficient team collaboration and outstanding code quality.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {UE4 Develop Engineer} % Job title
    {ZMVR(Xiamen Dream World Technology Co., Ltd.)} % Organization
    {Xiamen, China} % Location
    {Oct. 2021 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Committed to the continuous development and refactoring of game projects, achieving a significant leap in the player gaming experience, with an increase of up to 60\% in satisfaction.} 
        \item {Meticulously coordinated the allocation of work content requirements, ensuring the rational allocation and efficient utilization of team resources.} 
        \item {Deeply optimized game logic, significantly enhancing the game’s stability across various devices, creating a seamless virtual social space for players.} 
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
